\section{Introduction}

ITSs are perhaps the most anticipated smarty city services and have already seen widespread
adoption. The Sydney Coordinated Adaptive Traffic System (SCATS) is a fully adaptive urban
traffic control system that optimizes traffic flow and currently operates in more than 37,000
intersections worldwide (Citation). Optimizing traffic flow conditions not only shortens travel
times, but also can also reduce the carbon emissions generated from road vehicle activity
(Chong-White C., Millar M., Johnson F. and Shaw S. (2011). The evolution of the SCATS and
the environment study, Papers of the 34th Australasian transport research forum, Adelaide,
Australia.). Although there has been much research into the development of ITSs, most
approaches relied on mathematical equations and simulations. However, such approaches do not
encapsulate real world conditions such as weather, traffic accidents, and external events like
sports games (2-5 from here https://arxiv.org/ftp/arxiv/papers/1803/1803.02099.pdf). With the
advent of IoT, wireless sensor networks (WANs) and wireless sensor actuator networks
(WSANs) are being deployed to collect large-scale data of the physical world (Citation). Sensors
can collect data from cameras, inductor loops, GPS coordinates, etc. all in real-time. These
sensor networks record huge amounts data and then transmit this data to the cloud. Large-scale
analytics tools can then turn sensor data into decisions to optimize the operations of a city.

\section{Background}
\subsection{Traffic Flow Prediction}
\subsection{Xen}
\subsection{RT-Xen}
\section{Deep Learning for Traffic Flow Prediction}
\subsection{Dataset}
\subsection{LSTM}
\subsubsection{Training}
\section{Experimental Setup}
\section{Evaluation}
\section{Future Work}
\section{Conclusion}

